One Year HPC Certification Forum in Retrospective

### 2019-04-18 paper.tex
edited/extended the related work section

\jk{Please everyone!}

@@

In academia, many universities offer their own curriculum around scientific computing and HPC as part of their undergraduate programmes, covering a range of theoretical and practical aspects relevant to the students field of study, e.g. software development of numerical domain-specific applications.
Such courses rarely cover the efficient and effective use of HPC systems. 
The number of taught postgraduate courses focusing on HPC is small, and the number of the whole programmes dedicated to HPC is even smaller. % could probably list ~5

Data centres offer their own teaching materials and run a number of training courses to support their own users. 
Although, these are becoming more varied in content and more accessible through the adoption of online, remote and asynchronous delivery methods, they are still not enough to fulfil the training needs of our community. Due to a variety of reasons some training opportunities are still only available at a specific time or place, or simply do not scale well enough to satisfy the demand for them.

% ------------ Below not edited 
Several projects address the generation and sharing of teaching material for HPC.
The EuroLab-4-HPC project establishes training in form of (online) courses\footnote{\url{https://www.eurolab4hpc.eu/}}.
The Barcelona Supercomputing Centre (BSC) aims to develop a professional training curriculum \cite{sancho2016bsc}.
The virtual organization XSEDE\footnote{\url{https://portal.xsede.org/web/xup/training/overview}} provides an online system to train the usage of an HPC system, structuring the corresponding information on their website into major topics like “Getting Started”.
The user can navigate the topics and receive further information.

The SciNet Certificate Program
\footnote{\url{https://www.scinethpc.ca/scinet-certificate-program/}}
 provides course material for three major Computer Science topics: Scientific Computing, High Performance Computing, and Data Science each with several subcategories.
\footnote{\url{https://support.scinet.utoronto.ca/education/mods/certificate_programs_v2/index_public.php}}

Companies like NVIDIA are offering courses in deep learning\footnote{\url{https://www.nvidia.com/de-de/deep-learning-ai/education/}}.
Also Universities like Kennesaw State University providing Online Course for their students in the areas High Performance Computing and Big Data Analytics
\footnote{\url{https://ccse.kennesaw.edu/cs/programs/cert-hpcc.php}}.
\footnote{\url{https://www.ece.seas.gwu.edu/graduate-certificate-high-performance-computing}}

>>>>

@@

In academia, many universities offer their own curriculum around scientific computing and HPC, as part of their undergraduate programmes, covering a range of theoretical and practical aspects relevant to the students field of study, e.g. software development of numerical domain-specific applications.
Such courses rarely cover the efficient and effective use of HPC systems. 
The number of taught modules focusing on HPC is small, and the number of the whole programmes dedicated to HPC is even smaller. We are aware such programmes are run by: EPCC at the University of Edinburgh \footnote{\url{https://www.epcc.ed.ac.uk/msc}}, the University of Liverpool\footnote{\url{https://www.liverpool.ac.uk/study/postgraduate-taught/taught/big-data-msc/overview/}}, the International School for Advanced Studies (SISSA) and ICTP in Italy\footnote{\url{https://www.mhpc.it/}}, the Trinity Collage Dublin\footnote{\url{https://www.maths.tcd.ie/hpcmsc/}} in Ireland, the Polytechnic University of Catalonia\footnote{\url{https://masters.fib.upc.edu/masters/miri-high-performance-computing}} and BSC in Spain and the University of Cote d'Azur\footnote{\url{http://univ-cotedazur.fr/education/training?AIHPC18&lang=en}} in France. These 1-2 year master programmes are fully accredited by the universities that run them, but that also makes them fairly expensive and their comprehensiveness is not suitable for the majority of HPC users.

Data centres offer their own teaching materials and run a number of training courses to support their own users. 
Although, these are becoming more varied in content and more accessible through the adoption of online, remote and asynchronous delivery methods, they are still not enough to fulfil the training needs of our community. Due to a variety of reasons some training opportunities are still only available at a specific time or place, or simply do not scale well enough to satisfy the demand.

Several projects, organisations and initiatives continue to put their efforts into developing and sharing of teaching HPC resources. 
The EuroLab-4-HPC project establishes training in form of online courses\footnote{\url{https://www.eurolab4hpc.eu/}}.
The Barcelona Supercomputing Centre (BSC) aims to develop a professional training curriculum \cite{sancho2016bsc}.
Both XSEDE\footnote{\url{https://portal.xsede.org/web/xup/training/overview}} (The Extreme Science and Engineering Discovery Environment) and PRACE\footnote{\url{http://www.training.prace-ri.eu/}} (Partnership for Advanced Computing in Europa), serving similar purpose in US and Europe, provide a variety of training opportunities and resources to make HPC more accessible to researchers across many scientific domains.  
The SciNet Certificate Program\footnote{\url{https://www.scinethpc.ca/scinet-certificate-program/}} provides course material for three major Computer Science topics: Scientific Computing, High Performance Computing, and Data Science each with several subcategories.
Whereas the initiatives such as the HPC University\footnote{\url{http://hpcuniversity.org}}, the Carpentries (the HPC Carpentry especially)\footnote{\url{https://hpc-carpentry.github.io/}} and ACM SIGHPC Education Chapter\footnote{\url{https://sighpceducation.acm.org/}} strive to make sharing of teaching resources and practices simpler, and more accessible to trainers and practitioners alike.

Finally, many companies offer training courses making their products and services easier to use by their end-users, e.g. NVIDIA offering courses in deep learning\footnote{\url{https://www.nvidia.com/de-de/deep-learning-ai/education/}} or Arm offering courses on various arm technologies\footnote{\url{https://www.arm.com/support/training}}.
%Also Universities like Kennesaw State University providing Online Course for their students in the areas High Performance Computing and Big Data Analytics
%\footnote{\url{https://ccse.kennesaw.edu/cs/programs/cert-hpcc.php}}.
%\footnote{\url{https://www.ece.seas.gwu.edu/graduate-certificate-high-performance-computing}}  --> many universities do that, do we want to list all of them?
